R genes

### 2022-03-10 analysis/GOenrichment.Rmd
make the setup blocks nicer

```{r setup, include=FALSE}
library(topGO)
library(tidyverse)
library(rvest)
library(wesanderson)
library(httr)
library(stringi)
library(ggrepel)
library(eulerr)
library(UpSetR)
library(rrvgo)
library(kableExtra)
library(patchwork)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

>>>>

```{r setup, message=FALSE}
library(topGO)
library(tidyverse)
library(rvest)
library(wesanderson)
library(httr)
library(stringi)
library(ggrepel)
library(eulerr)
library(UpSetR)
library(rrvgo)
library(kableExtra)
library(patchwork)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

### 2022-03-10 analysis/GeneLossComparisonReads.Rmd
make the setup blocks nicer

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(wesanderson)
library(gghighlight)
library(patchwork)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

>>>>

```{r setup, message=FALSE}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(wesanderson)
library(gghighlight)
library(patchwork)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

### 2022-03-10 analysis/Orthofinder.Rmd
make the setup blocks nicer

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(wesanderson)
library(patchwork)
library(UpSetR)
library(kableExtra)
library(ggVennDiagram)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

>>>>

```{r setup, message=FALSE}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(wesanderson)
library(patchwork)
library(UpSetR)
library(kableExtra)
library(ggVennDiagram)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

### 2022-03-10 analysis/plotRgenes.Rmd
nicer table
make the setup blocks nicer

---
title: "R genes"
output: html_notebook
---
```{r setup}
library(tidyverse)
library(wesanderson)
library(ggtree)
library(ggtreeExtra)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

>>>>

---
title: "R genes"
output: html_notebook
---
```{r setup, message=FALSE}
library(tidyverse)
library(wesanderson)
library(ggtree)
library(ggtreeExtra)
library(kableExtra)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

# Quick summary stats

```{r}
df %>% group_by(Genome, Class) %>% summarise(sum=sum(Count)) %>% pivot_wider(names_from = c('Class'), values_from = sum) %>% kbl() %>% kable_styling()
```
